A Comparative Quality Metric for Fuzzing with Logic State Coverage

### 2024-02-26 paper/main.tex
discussion: semantic

>>>>

\pp{Semantically abnormal behaviors}
%
While the definition of program behaviors is separated from the output, it can
still incorporates \emph{semantically} abnormal behaviors (i.e., semantic bugs)
by means of exceptions. To be specific, semantic error detection such as
semantic sanitizers \cite{kim2019hydra,yun2016apisan} may capture semantic bugs
on the fly and make the behavior abnormal by terminating it. The definition
allows this as exceptions reference the data context before it is revealed to
the output.
